報告

### 2018-03-19 DiagrammeR/slide.Rmd
update

- **粗體**
- <div class="red2">蘋方?</div>

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

@@

@@

```{r echo=TRUE}
grViz('
digraph { //directed graph
    "總攻" -> "受";
    "強攻" -> "受";
    "健氣攻" -> "受";
     }'
)
```

>>>>

- **粗體**
- [紅色2]{.red2}
- [**color=red**]{style="color:#8A2BE2"}

<div class="error">
When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
</div>

@@

<div class="notes">
This is my *note*.

- It can contain markdown
- like this list

</div>

@@

```{r echo=TRUE}
grViz('
### <b>
digraph { //directed graph
### </b>
    "總攻" -> "受";
    "強攻" -> "受";
    "健氣攻" -> "受";
     }'
)
```

## Dataframe Printing
```{r}
knitr::kable(head(iris), align = "c", format = "markdown")
```
